
---
title: "MayaMD-Cleaning"
author: "Daniel Mejia"
date: '2022-06-25'
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(ggplot2)
library(tidyverse)
```

## MayaMD Analysis

This is document shows the analysis of the SVM PPHM_Citizens tested data file_1199 ORDERS_17May2022(1).xlsx

```{r data, include=TRUE}
data <- read_excel("MayaMD_1587.xlsx")
```

The document contains 1199 rows and 65 columns
All the data comes in character format. Based on the data from each attribute we consider the following data types:

### Categorical data
                   
- Gender
- Village
- Block
- District                                  
- Member.Id
- Family.Id                                 
- How.did.you.know.about.PPHM.
- Basophils
- Blood.Group

### Date data
- Test.Result.Arrived.On
- Date.of.birth
- Registered.On


### Numeric data
- BMI
- Weight
- Height
- Creatinine...Serum
- Eosinophils
- Hemoglobin
- Lymphocytes
- M.C.H.
- M.C.H.C
- M.C.V.
- Monocytes
- Neutrophils
- P.C.V.
- Platelet.count
- R.D.W..CV
- Random.Blood.Sugar
- T3..Tri.iodothyronine.
- T4..Thyroxine.
- TSH
- Total.RBC.Count
- Total.WBC.Count
- Vit.D.assay
- Vitamin.B12..Serum
- Folic.Acid.assay
- Uric.Acid...Serum
- A.G.Ratio
- Alanine.Transaminase..SGPT.ALT....Serum
- Albumin...Serum
- Alkaline.Phosphatase...Serum
- Aspartate.Transaminase..SGOT.AST....Serum
- Direct.Bilirubin...Serum
- Globulin...Serum
- HbA1c
- Indirect.Bilirubin...Serum
- Potassium
- SGOT...SGPT.Ratio
- Total.Bilirubin...Serum
- Total.Protein...Serum
- Triglyceride...Serum
- Vitamin.A.Retinol
- Total.Cholesterol...Serum
- Cholesterol...Serum
- HDL.Cholesterol...Serum
- LDL...HDL.Cholesterol.Ratio
- LDL.Cholesterol...Serum
- Total.Cholesterol...HDL.Cholesterol.Ratio
- VLDL.Cholesterol...Serum
- Prostate.Specific.Antigen..PSA.
- Blood.Urea
- Blood.Urea.Nitrogen
- Sodium
- Direct.Bilirubin


### Data Dimensions

```{r dimensions}
dim(data)
```

```{r head}
head(data)
```

### Convert to data frame
```{r convert_to_dataframe, echo=FALSE}
df <- data.frame(data)
```

### Convert numeric columns to numeric type
```{r convert1, echo=FALSE}
df_mod <- transform(df, Creatinine...Serum = as.numeric(Creatinine...Serum));
df_mod <- transform(df_mod, Eosinophils = as.numeric(Eosinophils));
df_mod <- transform(df_mod, Hemoglobin = as.numeric(Hemoglobin));

df_mod <- transform(df_mod, Lymphocytes = as.numeric(Lymphocytes));
df_mod <- transform(df_mod, M.C.H. = as.numeric(M.C.H.));
df_mod <- transform(df_mod, M.C.H.C = as.numeric(M.C.H.C));
df_mod <- transform(df_mod, M.C.V. = as.numeric(M.C.V.));
df_mod <- transform(df_mod,  Monocytes= as.numeric(Monocytes));
df_mod <- transform(df_mod, Neutrophils = as.numeric(Neutrophils));
df_mod <- transform(df_mod, P.C.V. = as.numeric(P.C.V.));
df_mod <- transform(df_mod, Platelet.count = as.numeric(Platelet.count));
df_mod <- transform(df_mod, R.D.W..CV = as.numeric(R.D.W..CV));
df_mod <- transform(df_mod,  Random.Blood.Sugar= as.numeric(Random.Blood.Sugar));

df_mod <- transform(df_mod,  T3..Tri.iodothyronine.= as.numeric(T3..Tri.iodothyronine.));
df_mod <- transform(df_mod,  T4..Thyroxine. = as.numeric(T4..Thyroxine.));

df_mod <- transform(df_mod, TSH = as.numeric(TSH));
df_mod <- transform(df_mod, Total.RBC.Count = as.numeric(Total.RBC.Count));
df_mod <- transform(df_mod, Total.WBC.Count = as.numeric(Total.WBC.Count));
df_mod <- transform(df_mod, Vit.D.assay = as.numeric(Vit.D.assay));
df_mod <- transform(df_mod, Vitamin.B12..Serum = as.numeric(Vitamin.B12..Serum));
df_mod <- transform(df_mod, Folic.Acid.assay = as.numeric(Folic.Acid.assay));
df_mod <- transform(df_mod, Uric.Acid...Serum = as.numeric(Uric.Acid...Serum));
df_mod <- transform(df_mod, A.G.Ratio = as.numeric(A.G.Ratio));
df_mod <- transform(df_mod, Alanine.Transaminase..SGPT.ALT....Serum = as.numeric(Alanine.Transaminase..SGPT.ALT....Serum));
df_mod <- transform(df_mod, Albumin...Serum = as.numeric(Albumin...Serum));
df_mod <- transform(df_mod, Alkaline.Phosphatase...Serum = as.numeric(Alkaline.Phosphatase...Serum));
df_mod <- transform(df_mod, Aspartate.Transaminase..SGOT.AST....Serum = as.numeric(Aspartate.Transaminase..SGOT.AST....Serum));
df_mod <- transform(df_mod, Direct.Bilirubin...Serum = as.numeric(Direct.Bilirubin...Serum));
df_mod <- transform(df_mod, Globulin...Serum = as.numeric(Globulin...Serum));
df_mod <- transform(df_mod, HbA1c = as.numeric(HbA1c));
df_mod <- transform(df_mod, Indirect.Bilirubin...Serum = as.numeric(Indirect.Bilirubin...Serum));
df_mod <- transform(df_mod, Potassium = as.numeric(Potassium));
df_mod <- transform(df_mod, SGOT...SGPT.Ratio = as.numeric(SGOT...SGPT.Ratio));
df_mod <- transform(df_mod, Total.Bilirubin...Serum = as.numeric(Total.Bilirubin...Serum));
df_mod <- transform(df_mod, Total.Protein...Serum = as.numeric(Total.Protein...Serum));
df_mod <- transform(df_mod, Triglyceride...Serum = as.numeric(Triglyceride...Serum));
df_mod <- transform(df_mod, Vitamin.A.Retinol = as.numeric(Vitamin.A.Retinol));
df_mod <- transform(df_mod, Total.Cholesterol...Serum = as.numeric(Total.Cholesterol...Serum));
df_mod <- transform(df_mod, Cholesterol...Serum = as.numeric(Cholesterol...Serum));
df_mod <- transform(df_mod, HDL.Cholesterol...Serum = as.numeric(HDL.Cholesterol...Serum));
df_mod <- transform(df_mod, LDL...HDL.Cholesterol.Ratio = as.numeric(LDL...HDL.Cholesterol.Ratio));
df_mod <- transform(df_mod, LDL.Cholesterol...Serum = as.numeric(LDL.Cholesterol...Serum));
df_mod <- transform(df_mod, Total.Cholesterol...HDL.Cholesterol.Ratio = as.numeric(Total.Cholesterol...HDL.Cholesterol.Ratio));
df_mod <- transform(df_mod, VLDL.Cholesterol...Serum = as.numeric(VLDL.Cholesterol...Serum));
df_mod <- transform(df_mod, Prostate.Specific.Antigen..PSA. = as.numeric(Prostate.Specific.Antigen..PSA.));
df_mod <- transform(df_mod, Blood.Urea = as.numeric(Blood.Urea));
df_mod <- transform(df_mod, Blood.Urea.Nitrogen = as.numeric(Blood.Urea.Nitrogen));
df_mod <- transform(df_mod, Sodium = as.numeric(Sodium));
df_mod <- transform(df_mod, Direct.Bilirubin = as.numeric(Direct.Bilirubin));
df_mod <- transform(df_mod, Total.Bilirubin = as.numeric(Total.Bilirubin));
```

```{r summary}
summary(df_mod)
```
## Data distribution

### BMI Histogram

```{r bmi, echo=FALSE}
df_mod %>% filter(!is.na(BMI)) %>% ggplot(aes(x=BMI)) + geom_histogram(alpha=0.5) 

```

### Weight Histogram

```{r hist_weight, echo=FALSE}
df_mod %>% filter(!is.na(Weight)) %>% ggplot( aes(x=Weight)) + geom_histogram(alpha=0.5, bins=10) 
```

### Heigth Histogram

```{r hist_height, echo=FALSE}
df_mod %>% filter(!is.na(Height)) %>% ggplot( aes(x=Height)) + geom_histogram(bins=10, alpha=0.5) 
```

### Creatinine...Serum

```{r histCreatinineSerum, echo=FALSE}
df_mod %>% filter(!is.na(Creatinine...Serum)) %>% ggplot(aes(x=Creatinine...Serum)) + geom_histogram(alpha=0.5, bins=10)

```

### Eosinophils

```{r hist_Eosinophilis, echo=FALSE}
df_mod %>%filter(!is.na(Eosinophils)) %>%  ggplot(aes(x=Eosinophils)) + geom_histogram(bins=10, alpha=0.5) 
```

### Hemoglobin

```{r hist_hemoglobin, echo=FALSE}
df_mod %>% filter(!is.na(Hemoglobin)) %>% ggplot(aes(x=Hemoglobin)) + geom_histogram(bins=10, alpha=0.5) 
```

## Creatinine...Serum
```{r Creatinine...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Creatinine...Serum)) %>% ggplot( aes(x=Creatinine...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Eosinophils
```{r Eosinophils, echo=FALSE}
df_mod %>% filter(!is.na(Eosinophils)) %>% ggplot(aes(x=Eosinophils)) + geom_histogram(bins=10, alpha=0.5)
```

## Hemoglobin
```{r Hemoglobin, echo=FALSE}
df_mod %>% filter(!is.na(Hemoglobin)) %>% ggplot( aes(x=Hemoglobin)) + geom_histogram(bins=10, alpha=0.5)
```

## Lymphocytes
```{r Lymphocytes, echo=FALSE}
df_mod %>% filter(!is.na(Lymphocytes)) %>% ggplot( aes(x=Lymphocytes)) + geom_histogram(bins=10, alpha=0.5)
```

## M.C.H.
```{r M.C.H., echo=FALSE}
df_mod %>% filter(!is.na(M.C.H.)) %>% ggplot(aes(x=M.C.H.)) + geom_histogram(bins=10, alpha=0.5)
```

## M.C.H.C
```{r M.C.H.C, echo=FALSE}
df_mod %>% filter(!is.na(M.C.H.C)) %>% ggplot( aes(x=M.C.H.C)) + geom_histogram(bins=10, alpha=0.5)
```

## M.C.V.
```{r M.C.V., echo=FALSE}
df_mod %>% filter(!is.na(M.C.V.)) %>% ggplot( aes(x=M.C.V.)) + geom_histogram(bins=10, alpha=0.5)
```

## Monocytes
```{r Monocytes, echo=FALSE}
df_mod %>% filter(!is.na(Monocytes)) %>% ggplot(aes(x=Monocytes)) + geom_histogram(bins=10, alpha=0.5)
```

## Neutrophils
```{r Neutrophils, echo=FALSE}
df_mod %>% filter(!is.na(Neutrophils)) %>% ggplot( aes(x=Neutrophils)) + geom_histogram(bins=10, alpha=0.5)
```

## P.C.V.
```{r P.C.V., echo=FALSE}
df_mod %>% filter(!is.na(P.C.V.)) %>% ggplot(aes(x=P.C.V.)) + geom_histogram(bins=10, alpha=0.5)
```

## Platelet.count
```{r Platelet.count, echo=FALSE}
df_mod %>% filter(!is.na(Platelet.count)) %>% ggplot(aes(x=Platelet.count)) + geom_histogram(bins=10, alpha=0.5)
```

## R.D.W..CV
```{r R.D.W..CV, echo=FALSE}
df_mod %>% filter(!is.na(R.D.W..CV)) %>% ggplot(aes(x=R.D.W..CV)) + geom_histogram(bins=10, alpha=0.5)
```

## Random.Blood.Sugar
```{r Random.Blood.Sugar, echo=FALSE}
df_mod %>% filter(!is.na(Random.Blood.Sugar)) %>% ggplot(aes(x=Random.Blood.Sugar)) + geom_histogram(bins=10, alpha=0.5)
```

## T3..Tri.iodothyronine.
```{r T3..Tri.iodothyronine., echo=FALSE}
df_mod %>% filter(!is.na(T3..Tri.iodothyronine.)) %>% ggplot(aes(x=T3..Tri.iodothyronine.)) + geom_histogram(bins=10, alpha=0.5)
```

## T4..Thyroxine.
```{r T4..Thyroxine., echo=FALSE}
df_mod %>% filter(!is.na(T4..Thyroxine.)) %>% ggplot(aes(x=T4..Thyroxine.)) + geom_histogram(bins=10, alpha=0.5)
```

## TSH
```{r TSH, echo=FALSE}
df_mod %>% filter(!is.na(TSH)) %>% ggplot( aes(x=TSH)) + geom_histogram(bins=10, alpha=0.5)
```

## Total.RBC.Count
```{r Total.RBC.Count, echo=FALSE}
df_mod %>% filter(!is.na(Total.RBC.Count)) %>% ggplot( aes(x=Total.RBC.Count)) + geom_histogram(bins=10, alpha=0.5)
```

## Total.WBC.Count
```{r Total.WBC.Count, echo=FALSE}
df_mod %>% filter(!is.na(Total.WBC.Count)) %>% ggplot( aes(x=Total.WBC.Count)) + geom_histogram(bins=10, alpha=0.5)
```

## Vit.D.assay
```{r Vit.D.assay, echo=FALSE}
df_mod %>% filter(!is.na(Vit.D.assay)) %>% ggplot( aes(x=Vit.D.assay)) + geom_histogram(bins=10, alpha=0.5)
```

## Vitamin.B12..Serum
```{r Vitamin.B12..Serum, echo=FALSE}
df_mod %>% filter(!is.na(Vitamin.B12..Serum)) %>% ggplot(aes(x=Vitamin.B12..Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Folic.Acid.assay
```{r Folic.Acid.assay, echo=FALSE}
df_mod %>% filter(!is.na(Folic.Acid.assay)) %>% ggplot( aes(x=Folic.Acid.assay)) + geom_histogram(bins=10, alpha=0.5)
```

## Uric.Acid...Serum
```{r Uric.Acid...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Uric.Acid...Serum)) %>% ggplot( aes(x=Uric.Acid...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## A.G.Ratio
```{r A.G.Ratio, echo=FALSE}
df_mod %>% filter(!is.na(A.G.Ratio)) %>% ggplot( aes(x=A.G.Ratio)) + geom_histogram(bins=10, alpha=0.5)
```

## Alanine.Transaminase..SGPT.ALT....Serum
```{r Alanine.Transaminase..SGPT.ALT....Serum, echo=FALSE}
df_mod %>% filter(!is.na(Alanine.Transaminase..SGPT.ALT....Serum)) %>% ggplot(aes(x=Alanine.Transaminase..SGPT.ALT....Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Albumin...Serum
```{r Albumin...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Albumin...Serum)) %>% ggplot(aes(x=Albumin...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Alkaline.Phosphatase...Serum
```{r Alkaline.Phosphatase...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Alkaline.Phosphatase...Serum)) %>% ggplot(aes(x=Alkaline.Phosphatase...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Aspartate.Transaminase..SGOT.AST....Serum
```{r Aspartate.Transaminase..SGOT.AST....Serum, echo=FALSE}
df_mod %>% filter(!is.na(Aspartate.Transaminase..SGOT.AST....Serum)) %>% ggplot(aes(x=Aspartate.Transaminase..SGOT.AST....Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Direct.Bilirubin...Serum
```{r Direct.Bilirubin...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Direct.Bilirubin...Serum)) %>% ggplot(aes(x=Direct.Bilirubin...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Globulin...Serum
```{r Globulin...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Globulin...Serum)) %>% ggplot(aes(x=Globulin...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## HbA1c
```{r HbA1c, echo=FALSE}
df_mod %>% filter(!is.na(HbA1c)) %>% ggplot( aes(x=HbA1c)) + geom_histogram(bins=10, alpha=0.5)
```

## Indirect.Bilirubin...Serum
```{r Indirect.Bilirubin...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Indirect.Bilirubin...Serum)) %>% ggplot(aes(x=Indirect.Bilirubin...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Potassium
```{r Potassium, echo=FALSE}
df_mod %>% filter(!is.na(Potassium)) %>% ggplot(aes(x=Potassium)) + geom_histogram(bins=10, alpha=0.5)
```

## SGOT...SGPT.Ratio
```{r SGOT...SGPT.Ratio, echo=FALSE}
df_mod %>% filter(!is.na(SGOT...SGPT.Ratio)) %>% ggplot( aes(x=SGOT...SGPT.Ratio)) + geom_histogram(bins=10, alpha=0.5)
```

## Total.Bilirubin...Serum
```{r Total.Bilirubin...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Total.Bilirubin...Serum)) %>% ggplot( aes(x=Total.Bilirubin...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Total.Protein...Serum
```{r Total.Protein...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Total.Protein...Serum)) %>% ggplot(aes(x=Total.Protein...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Triglyceride...Serum
```{r Triglyceride...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Triglyceride...Serum)) %>% ggplot( aes(x=Triglyceride...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Vitamin.A.Retinol
```{r Vitamin.A.Retinol, echo=FALSE}
df_mod %>% filter(!is.na(Vitamin.A.Retinol)) %>% ggplot(aes(x=Vitamin.A.Retinol)) + geom_histogram(bins=10, alpha=0.5)
```

## Total.Cholesterol...Serum
```{r Total.Cholesterol...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Total.Cholesterol...Serum)) %>% ggplot(aes(x=Total.Cholesterol...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Cholesterol...Serum
```{r Cholesterol...Serum, echo=FALSE}
df_mod %>% filter(!is.na(Cholesterol...Serum)) %>% ggplot(aes(x=Cholesterol...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## HDL.Cholesterol...Serum
```{r HDL.Cholesterol...Serum, echo=FALSE}
df_mod %>% filter(!is.na(HDL.Cholesterol...Serum)) %>% ggplot(aes(x=HDL.Cholesterol...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## LDL...HDL.Cholesterol.Ratio
```{r LDL...HDL.Cholesterol.Ratio, echo=FALSE}
df_mod %>% filter(!is.na(LDL...HDL.Cholesterol.Ratio)) %>% ggplot(aes(x=LDL...HDL.Cholesterol.Ratio)) + geom_histogram(bins=10, alpha=0.5)
```

## LDL.Cholesterol...Serum
```{r LDL.Cholesterol...Serum, echo=FALSE}
df_mod %>% filter(!is.na(LDL.Cholesterol...Serum)) %>% ggplot( aes(x=LDL.Cholesterol...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Total.Cholesterol...HDL.Cholesterol.Ratio
```{r Total.Cholesterol...HDL.Cholesterol.Ratio, echo=FALSE}
df_mod %>% filter(!is.na(Total.Cholesterol...HDL.Cholesterol.Ratio)) %>% ggplot(aes(x=Total.Cholesterol...HDL.Cholesterol.Ratio)) + geom_histogram(bins=10, alpha=0.5)
```

## VLDL.Cholesterol...Serum
```{r VLDL.Cholesterol...Serum, echo=FALSE}
df_mod %>% filter(!is.na(VLDL.Cholesterol...Serum)) %>% ggplot(aes(x=VLDL.Cholesterol...Serum)) + geom_histogram(bins=10, alpha=0.5)
```

## Prostate.Specific.Antigen..PSA.
```{r Prostate.Specific.Antigen..PSA., echo=FALSE}
df_mod %>% filter(!is.na(Prostate.Specific.Antigen..PSA.)) %>% ggplot( aes(x=Prostate.Specific.Antigen..PSA.)) + geom_histogram(bins=10, alpha=0.5)
```

## Blood.Urea
```{r Blood.Urea, echo=FALSE}
df_mod %>% filter(!is.na(Blood.Urea)) %>% ggplot(aes(x=Blood.Urea)) + geom_histogram(bins=10, alpha=0.5)
```

## Blood.Urea.Nitrogen
```{r Blood.Urea.Nitrogen, echo=FALSE}
df_mod %>% filter(!is.na(Blood.Urea.Nitrogen)) %>% ggplot(aes(x=Blood.Urea.Nitrogen)) + geom_histogram(bins=10, alpha=0.5)
```

## Sodium
```{r Sodium, echo=FALSE}
df_mod %>% filter(!is.na(Sodium)) %>% ggplot(aes(x=Sodium)) + geom_histogram(bins=10, alpha=0.5)
```

## Direct.Bilirubin
```{r Direct.Bilirubin, echo=FALSE}
df_mod %>% filter(!is.na(Direct.Bilirubin)) %>% ggplot(aes(x=Direct.Bilirubin)) + geom_histogram(bins=10, alpha=0.5)
```


# Null analysis

Most of the data has NULL values. In the following table is shown the percent of null values by attribute

```{r nullAnalysis}
nulos <- sapply(df_mod, is.na)
sumaNulos <- colSums(nulos[,-1])
sumaNulosDF <- data.frame(sumaNulos)
sumaNulosDF
``` 

```{r nullspct}
numrows <- nrow(df_mod)
pctNulos <- (sumaNulos / numrows) * 100.0
pctNulosDF <- data.frame(pctNulos)
pctNulosDF
```


# Categorical features

- Gender
- Village
- Block
- District                                  
- How.did.you.know.about.PPHM.
- Basophils
- Blood.Group

## Gender
```{r catGender}
df_mod %>% select(Gender) %>% group_by(Gender) %>% summarise(n = n())
```

## Village
```{r catVillage}
df_mod %>% select(Village) %>% group_by(Village) %>% summarise(n = n())
```

## Block
```{r catBlock}
df_mod %>% select(Block) %>% group_by(Block) %>% summarise(n = n())
```

## How.did.you.know.about.PPHM.
```{r catHow.did.you.know.about.PPHM.}
df_mod %>% select(How.did.you.know.about.PPHM.) %>% group_by(How.did.you.know.about.PPHM.) %>% summarise(n = n())
```

## Basophils
```{r catBasophils}
df_mod %>% select(Basophils) %>% group_by(Basophils) %>% summarise(n = n())
```

## Blood.Group
```{r catBlood.Group}
df_mod %>% select(Blood.Group) %>% group_by(Blood.Group) %>% summarise(n = n())
```



# Scatter Plots

```{r scatter1}

pairs(~BMI+Potassium+Direct.Bilirubin, data= df_mod)

```


```{r scatter1}

pairs(~BMI+Potassium+Direct.Bilirubin+Creatinine...Serum+Hemoglobin, data= df_mod)

```